How to compute the fusion product of MV cycles in type A

### 2021-05-17 draft.tex
my last changes reinstated

We will need the following definitions.
\begin{definition}
Let $ L \subset \CC[t]^m$ be a point in $ \Grth$.  We define the relative dimension of $L $ by
$$
\rdim(L) := \dim_\CC \CC[t]^m/L\,. 
$$
% 
If $ \gamma \subset \{1, \dots, m\}$, we define
\begin{gather*}
    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
L^\gamma:= L \cap \OO^\gamma \subset \OO^\gamma \quad L_\gamma := L / L^{\gamma^c} \subset \OO^\gamma
\end{gather*}
where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
\end{definition}

\acom{I started changing $\OO$ to $\CC[t]$ but we should rather change it to $R$ as we'll want this notation for $R = \CC[t]$ as well as $\cO$? Also, don't we want $L_\gamma = R^m/L^{\gamma^c}$}

\begin{lemma}
    For any $ L \in \Grth$ and any $ 
    \gamma \subset \{1, \dots, m\} $, we have $ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L$.
\end{lemma}
We let $ D_\gamma(L) := \rdim L_\gamma$. By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.

\jcom{There is a discrepancy regarding $ \gamma$ and $ \gamma^c$.}

\begin{lemma} \label{le:Srdim}
    Let $ L \in \Grth$.  The following are equivalent:
    \begin{enumerate}
        \item $ L \in S_+^\mu$
        \item $ \rdim L^{\{1, \dots, i\}} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $.
        \item $ \rdim L_{\{i+1, \dots, m\}} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$.
    \end{enumerate}
    The same statement hold for $ S_-^\mu$ with the $ L^\gamma$ changed to $ L_\gamma$ above.
\end{lemma}

@@

On the other hand, by definition 
$$
Z(\tau)_2 \subset \{ L \in S^\mu : L_{\{1, \dots, i\}} \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
$$
\acom{Need $L_{\{1,..,i\}}$ here.}

@@

Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
% 
\begin{theorem}
    \label{pr:govsasirrecs}
    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
\end{theorem}
% 
Given $A \in M_N(\CC)$ we denote by 
% $A\big|_{\CC^i}$ 
$A\big|_{\CC^p}$ 
the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$. If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. \acom{We could also use a more compact notation like $A_{(p)}$}
% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}

@@

\begin{proposition}
    % Given $b_{Z'},b_{Z''}\in\CC[N]$, 
    % Let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ 
    % be such that $t^{\lambda'}Z' = X(\tau')$ and $t^{\lambda''}Z'' = X(\tau'')$. 
    % and set $\mu = \mu' + \mu''$. If $s\ne 0$, then 
    The image of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ under the isomorphism of \Cref{th:OTGrW} is dense in $\mathring Z(\tau')\ast_{\CC^\times} \mathring Z(\tau'')$. 
    % \[
    % \overline{\phi(X(\tau',\tau''))} 
    % = Z'\ast_s Z'' \,. 
    % \]
\end{proposition}
% 
% \jcom{Do you want the ``blocky'' or ``boxy'' description here?  I mean, do you want $ i = 1, \dots, N$ or $ i =1, \dots, m$? I'm not so sure that ``boxy'' will work, since with those $s$ in the matrix, it doesn't preserves all the $ \CC^i$.}

@@

\begin{proof}
    % We wish to apply \Cref{prop:dth}. Nope
    % We will also need \Cref{le:Grl1l2}. Nope 
    % Consider the following diagram.
    % \[
    % \begin{tikzcd}
    %     X'\ast_s X'' \ar[r,dashed,"?"] \ar[d,"\bar g"] & X'\times X'' \ar[d," \phi\times \phi"] \\ 
    %     \Gr_{0,s}\ar[r,"\tau_s"] & \Gr\times\Gr
    % \end{tikzcd}
    % \]
    % \acom{Not sure what's a good notation for the vertical arrows. Don't want to introduce $\phi$. $\bar g(A) = g(A)\CC[t]^m$ temporarily.}
    % We show that the image of $\tau_s\circ \bar g$ coincides with the image of $\phi\times\phi$ which is dense in $Z'\times Z''$ by \Cref{prop:dth}.
    % % 
    Let $A\in X(\tau')\ast_s X(\tau'')$ and $i = 1,\dots, m$.  
    % Denote by 
    % $E_a$ the generalized $a$-eigenspace of $A$, and by 
    The lattices $L=g(A)\CC[t]^m$ and $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ are related by
    $$
    % L\cap \CC[t]^i = l
    l\cong L_{1,..,i}
    $$
    where $\CC[t]^i\subset\CC[t]^m = \CC^m\otimes_\CC\CC[t]$ denotes the $\CC[t]$-submodule generated by the first $i$ standard basis vectors.
    %

@@

\begin{corollary}
    $X'\ast_0 X''$ is a union of GOVs.
\end{corollary}
\begin{proof}
    Since $X'\ast_0 X''\subset \overline{\OO}^\lambda\cap\TT_\mu\cap\n$\dots 
\end{proof}

>>>>

@@

On the other hand, by definition 
$$
Z(\tau)_2 \subset \{ L \in S^\mu : L_{\{1, \dots, i\}} \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
$$

@@

Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
\begin{theorem}
    \label{pr:govsasirrecs}
    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
\end{theorem}
% 
% 
Given $A \in M_N(\CC)$ we denote by 
% $A\big|_{\CC^i}$ 
$A\big|_{\CC^p}$ 
the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$. If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. \acom{We could also use a more compact notation like $A_{(p)}$}
% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}

@@

\begin{proposition}
    The image of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ under the isomorphism of \Cref{th:OTGrW} is dense in $\mathring Z(\tau')\ast_{\CC^\times} \mathring Z(\tau'')$. 
    % \[
    % \overline{\phi(X(\tau',\tau''))} 
    % = Z'\ast_s Z'' \,. 
    % \]
\end{proposition}
% 
% \jcom{Do you want the ``blocky'' or ``boxy'' description here?  I mean, do you want $ i = 1, \dots, N$ or $ i =1, \dots, m$? I'm not so sure that ``boxy'' will work, since with those $s$ in the matrix, it doesn't preserves all the $ \CC^i$.}

@@

\begin{proof}
    % We wish to apply \Cref{prop:dth}. Nope
    % We will also need \Cref{le:Grl1l2}. Nope 
    % Consider the following diagram.
    % \[
    % \begin{tikzcd}
    %     X'\ast_s X'' \ar[r,dashed,"?"] \ar[d,"\bar g"] & X'\times X'' \ar[d," \phi\times \phi"] \\ 
    %     \Gr_{0,s}\ar[r,"\tau_s"] & \Gr\times\Gr
    % \end{tikzcd}
    % \]
    % \acom{Not sure what's a good notation for the vertical arrows. Don't want to introduce $\phi$. $\bar g(A) = g(A)\CC[t]^m$ temporarily.}
    % We show that the image of $\tau_s\circ \bar g$ coincides with the image of $\phi\times\phi$ which is dense in $Z'\times Z''$ by \Cref{prop:dth}.
    % % 
    Let $A\in X(\tau')\ast_s X(\tau'')$ and $i = 1,\dots, m$.  
    % Denote by 
    % $E_a$ the generalized $a$-eigenspace of $A$, and by 
    The lattices $L=g(A)\CC[t]^m$ and $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ are related by
    $$    
    % L\cap \CC[t]^i = l
    l = L_{1,..,i}
    $$
    where $\CC[t]^i\subset\CC[t]^m = \CC^m\otimes_\CC\CC[t]$ denotes the $\CC[t]$-submodule generated by the first $i$ standard basis vectors.
    %

@@

\begin{theorem}
    \label{pr:govsasirrecs}
    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{\overline{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
\end{theorem}
\acom{$\overline{X(\tau)}$ vs $Z(\tau) = \overline{al;sdj}$}
\begin{corollary}
    $X'\ast_0 X''$ is a union of GOVs.
\end{corollary}
\begin{proof}
    Since $X'\ast_0 X''\subset \overline{\OO}^\lambda\cap\TT_\mu\cap\n$\dots 
\end{proof}
